---
title: "testsolve"
author: "srihari"
date: "11 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Integer Programming

Objective Function
max: 8 x1 + 5 x2;

Constraints:
x1 + x2 <= 6;
9 x1 + 5 x2 <= 45;

#### Read file

```{r}
library(lpSolveAPI)
x <- read.lp("oct8.n1.lp")
```



### Solve the problem

```{r}
solve(x)
get.objective(x)
rsp1<-get.variables(x)
rsp1
```

```{r}
sp2 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp2, c(-8, -5))
add.constraint(sp2, c(1, 1), "<=", 6)
add.constraint(sp2, c(9, 5), "<=", 45)
add.constraint(sp2,c(1,0),">=",4)
```
```{r}
solve(sp2)
get.objective(sp2)
rsp2<-get.variables(sp2)
rsp2
```

```{r}
# SP 4 = SP 2 + x2 >= 2
sp4 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp4, c(-8, -5))
add.constraint(sp4, c(1, 1), "<=", 6)
add.constraint(sp4, c(9, 5), "<=", 45)
add.constraint(sp4,c(1,0),">=",4)
add.constraint(sp4,c(0,1),">=",2)
```
```{r}
solve(sp4)
get.objective(sp4)
rsp4<-get.variables(sp4)
rsp4
```
```{r}
# SP 5 = SP 2 + x2 <= 1
sp5 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp5, c(-8, -5))
add.constraint(sp5, c(1, 1), "<=", 6)
add.constraint(sp5, c(9, 5), "<=", 45)
add.constraint(sp5,c(1,0),">=",4)
add.constraint(sp5,c(0,1),"<=",1)
```
```{r}
solve(sp5)
get.objective(sp5)
rsp5<-get.variables(sp5)
rsp5
```
```{r}
# SP 6 = SP 5 + x1 >= 5
sp6 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp6, c(-8, -5))
add.constraint(sp6, c(1, 1), "<=", 6)
add.constraint(sp6, c(9, 5), "<=", 45)
add.constraint(sp6,c(1,0),">=",5)
add.constraint(sp6,c(0,1),"<=",1)
```
```{r}
solve(sp6)
get.objective(sp6)
rsp6<-get.variables(sp6)
rsp6
```
```{r}
# SP 7 = SP 5 + x1 <= 4
sp7 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp7, c(-8, -5))
add.constraint(sp7, c(1, 1), "<=", 6)
add.constraint(sp7, c(9, 5), "<=", 45)
add.constraint(sp7,c(1,0),"=",4)
add.constraint(sp7,c(0,1),"<=",1)
```
```{r}
solve(sp7)
get.objective(sp7)
rsp7<-get.variables(sp7)
rsp7
```
```{r}
sp3 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp3, c(-8, -5))
add.constraint(sp3, c(1, 1), "<=", 6)
add.constraint(sp3, c(9, 5), "<=", 45)
add.constraint(sp3,c(0,1),">=",3)
```
```{r}
solve(sp3)
get.objective(sp3)
rsp3<-get.variables(sp3)
rsp3
```

```{r}
sp8 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp8, c(-8, -5))
add.constraint(sp8, c(1, 1), "<=", 6)
add.constraint(sp8, c(9, 5), "<=", 45)
add.constraint(sp8,c(0,1),"<=",2)
```
```{r}
solve(sp8)
get.objective(sp8)
rsp8<-get.variables(sp8)
rsp8
```
```{r}
sp10 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp10, c(-8, -5))
add.constraint(sp10, c(1, 1), "<=", 6)
add.constraint(sp10, c(9, 5), "<=", 45)
add.constraint(sp10,c(1,0),"<=",3)
add.constraint(sp10,c(0,1),"<=",2)
```
```{r}
solve(sp10)
get.objective(sp10)
rsp10<-get.variables(sp10)
rsp10
```
```{r}
sp9 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp9, c(-8, -5))
add.constraint(sp9, c(1, 1), "<=", 6)
add.constraint(sp9, c(9, 5), "<=", 45)
add.constraint(sp9,c(1,0),">=",4)
add.constraint(sp9,c(0,1),"<=",2)
```
```{r}
solve(sp9)
get.objective(sp9)
rsp9<-get.variables(sp9)
rsp9
```
```{r}
sp11 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp11, c(-8, -5))
add.constraint(sp11, c(1, 1), "<=", 6)
add.constraint(sp11, c(9, 5), "<=", 45)
add.constraint(sp11,c(1,0),">=",4)
add.constraint(sp11,c(0,1),">=",2)
```
```{r}
solve(sp11)
get.objective(sp11)
rsp11<-get.variables(sp11)
rsp11
```

```{r}
sp12 <- make.lp(0, 2) # number of constraints, number of decision variables
set.objfn(sp12, c(-8, -5))
add.constraint(sp12, c(1, 1), "<=", 6)
add.constraint(sp12, c(9, 5), "<=", 45)
add.constraint(sp12,c(1,0),">=",4)
add.constraint(sp12,c(0,1),"<=",1)
```
```{r}
solve(sp12)
get.objective(sp12)
rsp12<-get.variables(sp12)
rsp12
```



### Print the solution

```{r}
library(lpSolveAPI)
rsp1
rsp2
rsp3
rsp4
rsp5
rsp6
rsp7
rsp8
rsp9
rsp10
rsp11
rsp12
x1<-c(3.75,3,4,4.44,4,5,3.88,3,3.88,4,4)
x2<-c(2.25,3,1.8,1.8,1,0,2,3,2,1.8,1.8)
z<-c(41.25,39,41,40.5,37,40,41.11,39,34,41,40.55)
plot(x1,x2,col="blue", pch=19, cex=2)
text(x1,x2, labels=0:25, pos=3)
points(x=3,y=3,col="red",pch=19, cex=2)
points(x=4,y=1,col="red",pch=19, cex=2)
points(x=3,y=2,col="red",pch=19, cex=2)
points(x=5,y=0,col="red",pch=19, cex=2)
```
