---
title: "Model Evaluation using The Test Data"
output:
  html_document:
    df_print: paged
---

```{r library, warning=F, message=F}
library(readxl)
library(reshape2)
library(dplyr)
library(magrittr)
library(tm)
library(keras)
library(caret)
library(SnowballC)
```

## 1. Loading The Test Data

```{r load-dataset, warning=F, message=F, echo = T, results = 'hide'}
# Encode specific kinds of values as NA while reading excel
# Treat all columns as character

feb_test_df <- read.csv("february_test_dataset.csv", na = c("", "---"), col_types = "text")
```

### 1.1 Removing 

```{r, echo=FALSE}
features_to_rm <- c(
  "SR.Number",
  "SR.Address.Line.1",
  "SR.State",
  "SR.City",
  "SR.Site",
  "SR.Status",
  "SR.Contact.Date",
  "SR.Coverage.Hours",
  "SR.Coverage.Hours.1",
  "Activity.Status",
  "Charges.Status",
  "Br.Area.Desc",
  "Base.Call.YN",
  "Activity.Facts.Call.Num",
  "Activity.Completed.Date",
  "Item.Desc",
  "SR.Serial.Number"
)

features_to_rm
```

```{r}
feb_test_df <- feb_test_df %>% dplyr::select(-c(features_to_rm_test))

glimpse(feb_test_df)
```

## 2. Cleaning The Data

### 2.1 Encoding The Variables as Factors

We can notice that R has miss categorized some of the features in our dataset. There are certain features that are supposed to be read as categorical such as:

```{r echo=FALSE}
char_to_factors <- c(
 "ï..Invoiced..Y.N.",
  "Activity.Type" ,
 "Activity.Trouble.Code" ,
 "Coverage.Type" ,
"SR.Type" ,
 "SR.Device",
  "SR.Owner..Q.." ,
  "Br.Branch.Desc",
  "Br.Region.Desc",
   "Cash.Vendor...Consumable.Contracts"
)

char_to_factors
```

Lets encode the features in `char_to_factors` as factors

```{r}
feb_test_df <- feb_test_df %>% mutate_at(char_to_factors_test, factor)

glimpse(feb_test_df)
```

### 2.2 Preprocessing Free Form Text

The features in our dataset that are free form text are the features `Billing.Notes` and `Call.Text`.

Below is a preview of `Call.Text`

```{r}
feb_test_df$`Call.Text` %>% head(3)
```

Below is a preview of `Billing.Notes`

```{r}
feb_test_df$`Billing.Notes` %>% extract(c(3, 5, 1))
```

```{r}
call_text_test <-  use_series(feb_test_df, `Call.Text`)
billing_notes_test <-  use_series(feb_test_df, `Billing.Notes`)
```

```{r}
call_text_corpus_test <- VCorpus(VectorSource(call_text_test), readerControl = list(language = "en"))
bill_notes_corpus_test <- VCorpus(VectorSource(billing_notes_test), readerControl = list(language = "en"))
```

```{r}
call_text_corpus_test %>% extract(1:3) %>% inspect()
```

```{r}
call_text_corpus_test %>% head(3) %>% lapply(function (doc) doc$content)
```

To clean our data set we will have to: 

* Convert the text to lower case, so that words like "write" and "Write" are considered the same word
* Remove numbers
* Remove English stopwords e.g "the", "is", "of", etc.
* Remove punctuation e.g ",", "?", etc.
* Eliminate extra white spaces
* Stemming our text 

Using the `tm` package we will apply transformations to each text document in the `call_text_corpus` to clean the text document.

```{r}
replace_asterix <- function(document) {
  gsub(pattern = "\\*", replacement = " ", document)
}

add_space_period <- function(document) {
  gsub(pattern = "\\.", replacement = ". ", document)
}

remove_single_chars <- function(document) {
  gsub(pattern = "\\s[a-z]\\s", replacement = " ", document)
}

clean_up <- function(corpus) {
  corpus %>% 
    # Convert the text to lower case
    tm_map(content_transformer(tolower)) %>%
    # Replace asterics "*" with an empty space
    tm_map(content_transformer(replace_asterix)) %>%
    # Add a space after a period
    tm_map(content_transformer(add_space_period)) %>%
    # Remove numbers
    tm_map(removeNumbers) %>%
    # Remove english common stopwords
    tm_map(removeWords, stopwords("english")) %>%
    # Remove words related to time
    tm_map(removeWords, c("pm", "am", "edt")) %>%
    # Remove punctuations
    tm_map(removePunctuation) %>%
    # Remove orphaned letters
    tm_map(content_transformer(remove_single_chars)) %>%
    # Eliminate extra white spaces
    tm_map(stripWhitespace) %>%
    # strip trailing and leading whitespace
    tm_map(content_transformer(trimws)) %>%
    # Stem words
    tm_map(stemDocument)
}

call_text_cleaned_test <- clean_up(call_text_corpus_test)
bill_notes_cleaned_test <- clean_up(bill_notes_corpus_test)
```


```{r}
call_text_cleaned_test  %>% lapply(function (doc) doc$content) %>% extract(1:5)
```

```{r}
bill_notes_cleaned_test %>% lapply(function (doc) doc$content) %>% extract(1:5)
```

```{r}
feb_test_df$`Call.Text` <- call_text_cleaned_test %>% sapply(function (doc) doc$content)
feb_test_df$`Billing.Notes` <- bill_notes_cleaned_test %>% sapply(function (doc) doc$content)
```

## 3. Tokenization & Encoding

```{r constants}
CONSTANTS <- list(
  # We will only consider the top MAX_WORDS in the dataset
  MAX_WORDS = 20000,
  # We will cut text after MAX_LEN
  MAX_LEN = 200,
  BATCH_SIZE_GPU = 256,
  BATCH_SIZE_CPU = 128
)
```

### 3.1 Encoding Categorical data



#### 3.1.1 One Hot Encoding The Categorical Variables

```{r}
categorical_vars_test <- feb_test_df %>% 
  dplyr::select(char_to_factors_test) %>%
  # Treat NAs as a factor
  mutate_all(addNA)

glimpse(categorical_vars_test)
```

```{r one-hot-encoding}
 
dummy_model_test <- dummyVars(" ~ .", data = categorical_vars_test, fullRank = T)
auxillaries_feb_test <- data.matrix(predict(dummy_model_test, newdata = categorical_vars_test))
padded_auxillaries <- cbind(auxillaries_feb_test, matrix(0, nrow = 108873, ncol = 29))
cat('Shape of auxillary tensor:', dim(padded_auxillaries), "\n")
```


### 3.2 Tokenizing Free Form Text

We will tokenize each free form text: `Call.Text` and `Billing.Notes` separately. 

#### 3.2.1 Call.Text

We will start out by tokenizing `Call.Text`:

A `tokenizer` object will be created and configured to only take into account the top most common words, then builds the word index. We then turn the texts into lists of integer indices.

```{r}
call_text_test_df <- feb_test_df %>% dplyr::select(c("Call.Text"))

call_text_tokenizer_test <- text_tokenizer(num_words = CONSTANTS$MAX_WORDS) %>% 
  fit_text_tokenizer(call_text_test_df$`Call.Text`)

call_text_sequences_test <- texts_to_sequences(call_text_tokenizer_test, call_text_test_df$`Call.Text`)
```

```{r}
call_text_word_index_test <- call_text_tokenizer_test$word_index

cat("Found", length(call_text_word_index_test), "unique tokens.\n")
```

```{r}
call_text_test_data <- pad_sequences(call_text_sequences_test, maxlen = CONSTANTS$MAX_LEN)

cat("Shape of data tensor:", dim(call_text_test_data), "\n")
```

#### 3.2.2 Billing.Notes

We then tokenize `Billing.Notes`:

```{r}
billing_notes_test_df <- feb_test_df %>% dplyr::select("Billing.Notes")

billing_notes_tokenizer_test <- text_tokenizer(num_words = CONSTANTS$MAX_WORDS) %>% 
  fit_text_tokenizer(billing_notes_test_df$`Billing.Notes`)

billing_notes_sequences_test <- texts_to_sequences(
  billing_notes_tokenizer_test,
  billing_notes_test_df$`Billing.Notes`
)
```

```{r}
billing_notes_word_index_test <- billing_notes_tokenizer_test$word_index

cat("Found", length(billing_notes_word_index_test), "unique tokens.\n")
```

```{r}
billing_notes_test_data <- pad_sequences(billing_notes_sequences_test, maxlen = CONSTANTS$MAX_LEN)

cat("Shape of data tensor:", dim(billing_notes_test_data), "\n")
```

## 4. Training Model on February Test Data

```{r}
feb_pred_probs <- predict(model,
    list(call_text_test_data, billing_notes_test_data, padded_auxillaries),
    batch_size = CONSTANTS$BATCH_SIZE_CPU
  )

feb_pred_class <- as.numeric(feb_pred_probs >= .25) %>% as.factor() %>% as.data.frame()

colnames(feb_pred_class) <- c("Invoiced (Y/N)")
write.csv(feb_pred_class, file = "Prediction file.csv", row.names = F)
```

