---
title: "Returs_to_scale_CRS,DRS,IRS,VRS,FDH,FRH"
author: "srihari"
date: "21 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Geetting library, input and output

```{r}
library(Benchmarking)
library(ucminf)
library(lpSolveAPI)
inp<- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2.0,1.2,0.7),ncol = 2)
out <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
```

### Displaying INPUT as inp and OUTPUT as out
```{r}
inp
out
colnames(inp) <- c("staff_HRS_Per_day","Supplies_Day")
colnames(out) <- c("reimursed_p_day","private_p_day")
```
### DEA analysis of CRS
```{r}
crs<- dea(inp,out, RTS ='CRS')
crs
peers(crs)
lambda(crs)
```
### Plotting CRS
```{r}
dea.plot.frontier(inp,out,RTS = 'crs',xlab = 'input', ylab ='output',main ='Input vs Output using CRS')
```
### DEA analysis of DRS
```{r}
drs<- dea(inp,out, RTS ='drs')
drs
peers(drs)
lambda(drs)
```
### Plotting DRS
```{r}
dea.plot.frontier(inp,out,RTS = 'drs',xlab = 'input', ylab ='output',main ='Input vs Output using DRS')
```
### DEA analysis of IRS
```{r}
irs<-dea(inp,out, RTS ='irs')
irs
peers(irs)
lambda(irs)
```
### Plotting IRS
```{r}
dea.plot.frontier(inp,out,RTS = 'irs',xlab = 'input', ylab ='output',main ='Input vs Output using IRS')
```

### DEA analysis of VRS
```{r}
vrs<-dea(inp,out, RTS ='vrs')
vrs
peers(vrs)
lambda(vrs)
```
### Plotting VRS
```{r}
dea.plot.frontier(inp,out,RTS = 'vrs',xlab = 'input', ylab ='output',main ='Input vs Output using VRS')
```
### DEA analysis of FRH
```{r}
frh<- dea(inp,out, RTS ='add')
frh
peers(frh)
lambda(frh)
```
### Plotting FDH/ADD

```{r}
fdh<-dea(inp,out, RTS ='fdh')
fdh
peers(fdh)
lambda(fdh)
```

```{r}
dea.plot.frontier(inp,out,RTS = 'fdh',xlab = 'input', ylab ='output',main ='Input vs Output using fdh')
```


dea.plot.frontier(inp,out,RTS = 'add',xlab = 'input', ylab ='output',main ='Input vs Output using frh')
```
```{r}
```

### Tabular view or results for CRS,DRS,IRS,VRS,FDH,FRH
```{r}
crs<- c(1.0000, 1.0000 ,1.0000, 1.0000, 0.9775, 0.8675)
drs<- c(1.0000, 1.0000 ,1.0000, 1.0000, 0.9775, 0.8675)
irs<- c(1.0000, 1.0000, 1.0000, 1.0000, 1.0000, 0.8963)
fdh<- c( 1 ,1 ,1 ,1 ,1 ,1)
vrs<- c(1.0000, 1.0000, 1.0000, 1.0000, 1.0000, 0.8963)
frh<- c(1, 1, 1, 1, 1, 1)
facility<-c('facility 1','facility 2','facility 3','facility 4','facility 5', 'facility 6')
results<-data.frame(facility,crs,drs,fdh,irs,vrs,frh)
results
```
